Selección de Servicios Web De Máxima Utilidad Usando Circuitos

### 2009-12-13 tesis/propuesta/propuesta_iae.tex
avance de traduccion a español de propuesta hasta motivacion

  \documentclass{llncs}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage[boxed]{algorithm2e}
\usepackage{amssymb}
\usepackage[pdftex]{graphicx}
\usepackage{enumerate}
\DeclareGraphicsExtensions{.jpg, .png, .mps, .bmp, .pdf}
\usepackage{epsfig}
\usepackage{subfigure}
\newtheorem{Definition}{Definition} 
\newtheorem{Example}{Example} 
\newtheorem{Theorem}{Theorem} 
\newtheorem{Proof}{Proof} 
\newcommand{\denselist}{\topsep 0pt \itemsep -4pt}
\newcommand{\tup}[1]{\langle #1 \rangle}
\newcommand{\vvec}[1]{\mathbf{#1}}
\newcommand{\join}{\bowtie}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\body}{{body}}
\newcommand{\head}{{head}}
\newcommand{\qrule}{:\!\!-}
\newcommand{\arc}{\text{arc}}
\newcommand{\Theory}[1]{T(#1)}
\newcommand{\mcdsat}{\textsc{McdSat}}
\newcommand{\minicon}{{MiniCon}}
\newcommand{\Omit}[1]{}
\newcommand{\citeX}[1]{\citeauthor{#1}~\citeyear{#1}}

\begin{document}
\allowdisplaybreaks
\title{Selecting the Maximum-Utility  Web Services  Using Circuits}
\author{Daniel Izquierdo \inst{1}  and Blai Bonet \inst{1}  and Mar\'{\i}a-Esther Vidal \inst{1}}

\institute{Universidad Sim\'on Bol\'{\i}var\\
                Caracas, Venezuela\\
                \{idaniel,bonet,mvidal\}ldc.usb.ve} \maketitle
\begin{abstract}
In Service Oriented Architectures (SOA), concrete services are described in terms of functionality   and QoS parameters, while software applications are specified as workflows of abstract services and non-functional criteria that establish the  application desirable functionality and  expected quality, respectively.  During workflow execution time,  abstract services  are rewritten 
with the concrete services  that meet the workflow  functional and non-functional restrictions. Since, service selection is done on-the-flight and the space of concrete services may be very large, efficiency and scalability are required.  In this paper we propose the {\it McdSat}$^c$ framework to efficiently solve the problem of service selection in presence of a large number of concrete services.
First, we use the Local As View approach to describe the functionality  of the concrete services in terms of views of abstract services, the quality as an overall utility function that combines the different QoS values that describe the service, and  workflows as  conjunctive queries on abstract services. Based on this representation, we 
model the problem of service selection as a known problem in the area of integration systems referred as query rewriting using views.  We encode the service selection problem as a propositional theory whose models correspond to the composition of the services that implement the abstract workflow and maximizes the overall utility function; known relationships between d-DNNF theories and arithmetic circuits are exploited to provide an efficient and scalable solution.  We report on the performance of our proposed approach, and we observe that  {\it McdSat}$^c$  efficiently scales up to large instances of the service selection problem.

\end{abstract}                
\section{Introduction}
Under the umbrella of the Semantic Web and supported by Service Oriented architectures, the number of Web data sources and services has exploded during the last few years.  For example,  currently, the molecular biology databases
collection includes 1,170 databases~\cite{Galperin09}, that is
95 more than the previous year~\cite{Galperin2008} and 110 more than two years ago~\cite{Galperin2007};  tools
and services as well as the number of instances published by these resources, follow a similar progression~\cite{Benson07}. Thanks
to this wealth, users rely more on various
digital tasks such as data retrieval from public data sources and
data analysis with Web tools or services organized in
complex workflows.

In order to design an application, users usually specify the functionality in terms of a workflow of abstract services, while the desirable quality  is defined by restricting the values of the QoS parameters that describe the concrete available services. To evaluate the proposed workflow,  abstract services are instantiated on concrete services in a way restrictions on the QoS parameters are satisfied.  However, the performance of this tasks is impacted by the number of available sources,  techniques enable to efficiently scale up to a large number of services are required.

In this paper we aim to provide a solution to this problem and provide techniques that efficiently traverse the space of available services and select combinations that meet the functional and non-functional requirements that describe a designed application.  We name our proposed solution {\it MCDSat}$^c$.

In {\it MCDSat}$^c$, concrete service functionalities are decribed as views on abstract services and workflows are represented as conjunctive queries on abstract services; this service representation is similar to the one generated in a semi-automatic way for the {\cal DEIMOS} system ~\cite{AmbiteISWC09}.  In addition, rules that define workflows and  concrete services in the {\it MCDSat}$^c$ catalog,  are created in a way that input and output restrictions of the combined abstract services are satisfied. To represent the QoS measures, each concrete service description is annotated with a real number that represents an overall value of the QoS measures of this service.  Finally, {\it MCDSat}$^c$ models the web service selection problem as the problem of query rewriting using views \cite{halevy:survey}. This problem is important in the context of data integration
\cite{Chen05,JaudoinPRST05}, and query optimization and data maintenance \cite{AfratiLU07,levy:bucket}, and several approaches have been defined to efficiently scale up to a large number of views~\cite{arvelo:aaai06,pods:DuschkaG97,sac:DuschkaG97,levy:bucket,pottinger:minicon}. In this paper we propose the {\it MCDSat}$^c$ framework which extends the approach proposed in ~\cite{arvelo:aaai06},  with the capability of dealing with constants and identifying the composition of services that maximizes a given utility function.

{\it MCDSat}$^c$  translates an instance of the service selection problem into the problem of enumerating the models of a propositional theory that encodes information about the workflow, the concrete services and the conditions that need to be satisfied in order to generate a composition that maximizes the utility function. This theory is represented as a CNF formula which is compiled into a deterministic
and decomposable negation normal form d-DNNF representation, from which the models that maximizes the overall utility function are obtained in linear time using modern SAT techniques~\cite{darwiche:dnnf}.   
We empirically studied the quality of the {\it MCDSat}$^c$ on variety of benchmarks and we observed  that the proposed technique provides an efficient solution to the service selection problem which is able to scale up to large workflows as well to a large number of views.

@@

\section{Motivating Example}
Consider the abstract and concrete services in Table ~\ref{table:services}  which represent applications in the flight domain.

\begin{table}
\begin{tabular}{| l| l |}
\hline
Abstract Service & Description \\
\hline
$fight(x1,x2)$ & relates cities x1 and x2 if there is a flight between them\\
\hline
$uscity(x1)$ &  determines if a city x1 is a US city\\
\hline \hline
Concrete  Service & Description \\
\hline
$national(x1,y1)$&  returns  two US cities that are connected by  direct flights \\
\hline
$oneway(x1,y1)$ & returns two cites that are connected by one way direct flights \\
\hline
$onestop(x1,y1)$ &  returns  two cites that are connected by one-stop flights \\
\hline
$ flightToCCS(x1,"CCS")$ & returns a city that is connected to  Caracas by a direct flight\\
 \hline
$ onestopToCCS(x1,y1)$ & returns two cites x1 and y1, such that there is  one-stop flight\\ 
 & from city x1 to Caracas stopping at city y1.\\
 \hline
 $fromWAS("WAS",y1)$ &  returns a city y1 to which flights from Washington arrive. \\
 \hline
\end{tabular}
\label{table:services}
\caption{Abstract and Concrete Services}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=8cm]{odd}
\caption{A decomposable and deterministic NNF.}
\label{fig:dnnf}
\end{figure}

@@

In order to do so, the theory $\Theory{\Q}$ is transformed into a d-DNNF
theory $\Delta(\Q)$ with a CNF to d-DNNF compiler.
The compiler's algorithm is similar to the DPLL algorithm
for SAT but enhanced with advanced techniques such as clause
learning and caching.
\begin{figure}
\centering
\includegraphics[width=10cm]{mdcsatC.pdf}
\caption{The McdSat$^c$ Architecture}
\label{fig:dnnf}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=8cm]{plot1.pdf}
\caption{Compilation Time Benchmark I}
\label{fig:plot1}
\end{figure}

>>>>

  \documentclass{llncs}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage[boxed]{algorithm2e}
\usepackage{amssymb}
\usepackage[pdftex]{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage{enumerate}
\DeclareGraphicsExtensions{.jpg, .png, .mps, .bmp, .pdf}
\usepackage{epsfig}
\usepackage{subfigure}
\newtheorem{Definition}{Definition} 
\newtheorem{Example}{Example} 
\newtheorem{Theorem}{Theorem} 
\newtheorem{Proof}{Proof} 
\newcommand{\denselist}{\topsep 0pt \itemsep -4pt}
\newcommand{\tup}[1]{\langle #1 \rangle}
\newcommand{\vvec}[1]{\mathbf{#1}}
\newcommand{\join}{\bowtie}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\body}{{body}}
\newcommand{\head}{{head}}
\newcommand{\qrule}{:\!\!-}
\newcommand{\arc}{\text{arc}}
\newcommand{\Theory}[1]{T(#1)}
\newcommand{\mcdsat}{\textsc{McdSat}}
\newcommand{\minicon}{{MiniCon}}
\newcommand{\Omit}[1]{}
\newcommand{\citeX}[1]{\citeauthor{#1}~\citeyear{#1}}

\begin{document}
\allowdisplaybreaks
\title{Selección de Servicios Web De Máxima Utilidad Usando Circuitos}
\author{Daniel Izquierdo}

\institute{Universidad Sim\'on Bol\'{\i}var\\
                Caracas, Venezuela\\
                idaniel@ldc.usb.ve} \maketitle
\begin{abstract}
En las arquitecturas orientadas a servicios (SOA), los servicios concretos se
describen en términos de parámetros de funcionalidad y calidad de servicio,
mientras que las aplicaciones de \emph{software} se especifican como flujos de
trabajo de servicios abstractos y criterios no-funcionales que establecen la
funcionalidad deseada y la calidad esperada respectivamente. En tiempo de
ejecución de un flujo de trabajo, los servicios abstractos se reescriben con los
servicios concretos que cumplen con las restricciones funcionales y no
funcionales del flujo de trabajo. Dado que la selección de los servicios es
hecha al momento y el espacio de servicios concretos puede ser muy grande, se
requiere eficiencia y escalabilidad. En este trabajo se propone la
infraestructura {\it McdSat}$^c$ para resolver eficientemente el problema de
selección de servicios en presencia de un número grande de servicios concretos.
En primer lugar se utiliza la aproximación \emph{Local As View} para describir
la funcionalidad de los servicios concretos en términos de vistas de servicios
abstractos, la calidad como una función de utilidad general que combina los
distintos valores de calidad que describen cada servicio, y los flujos de
trabajo como consultas conjuntivas sobre servicios abstractos. Basándose en esta
representación, se modela el problema de selección de servicios como un problema
conocido en el área de integración de sistemas conocido como reescritura de
consultas usando vistas. Codificamos el problema de selección de servicios como
una teoría proposicional cuyos modelos corresponden a la composición de los
servicios que implementan el flujo abstracto; se explotan relaciones conocidas
entre teorías d-DNNF y circuitos aritméticos para proveer una solución eficiente
y escalable. Se reporta sobre el rendimiento de la aproximación propuesta y se
observa que  {\it McdSat}$^c$  escala a instancias grandes del problema de
selección de servicios.

\end{abstract}                
\section{Introducción}
Bajo la sombra de la Web Semántica y con el apoyo de arquitecturas orientadas a
servicios, el número de fuentes de datos y servicios Web ha explotado en los
últimos años. Por ejemplo, actualmente la colección de bases de datos de
biología molecular incluye 1.170 bases de datos~\cite{Galperin09}, lo cual es 95
más que el año pasado~\cite{Galperin2008} y 110 más que hace dos
años~\cite{Galperin2007}. Tanto las herramientas y servicios como el número de
instancias publicadas por estos recursos siguen una progresión
similar~\cite{Benson07}. Gracias a este tesoro de datos, los usuarios se apoyan
más en varias tareas digitales como obtención de datos de fuentes públicas y
análisis de datos con herramientas o servicios Web organizados en flujos de
trabajo complejos.

Para diseñar una aplicación, los usuarios frecuentemente especifican la
funcionalidad en términos de un flujo de trabajo de servicios abstractos,
mientras que la calidad deseada se define restringiendo los valores de los
parámetros QoS (calidad de servicio) que describen los servicios concretos
disponibles. Para evaluar el flujo propuesto, se instancian los servicios
abstractos con concretos de manera que se satisfagan las restricciones sobre
parámetros QoS. Sin embargo, el rendimiento de estas tareas es impactado por el
número de fuentes disponibles. Se requieren técnicas que permitan escalar
eficientemente a un número grande de servicios.

En este trabajo se intenta proponer una solución a este problema y proveer
técnicas que recorran eficientemente el espacio de servicios disponibles y
seleccionen combinaciones que cumplan con los requerimientos funcionales y
no-funcionales que describen una aplicación diseñada. Se llama 
{\it MCDSat}$^c$ a la solución propuesta.

En {\it MCDSat}$^c$, las funcionalidades de servicios concretos se describen
como vistas sobre servicios abstractos y los flujos de trabajo se representan
como consultas conjuntivas sobre servicios abstractos; esta representación de
los servicios es similar a la generada de manera semiautomática para el
sistema {\cal DEIMOS}~\cite{AmbiteISWC09}. Adicionalmente, las reglas
que definen flujos de trabajo y servicios concretos en el catálogo de
{\it MCDSat}$^c$ son creadas de manera que las restricciones de entrada y salida
de los servicios abstractos combinados sean satisfechas. Para representar las
medidas de QoS, cada descripción de servicio concreto es anotada con un número
real que representa un valor general para las medidas de QoS del servicio en
particular. Finalmente, {\it MCDSat}$^c$ modela el problema de selección de
servicios web como el problema de reescritura de consultas usando vistas
\cite{halevy:survey}. Este problema es importante en el contexto de integración
de datos \cite{Chen05,JaudoinPRST05} y de optimización de consultas y
mantenimiento de datos \cite{AfratiLU07,levy:bucket} y se han definido varias
aproximaciones para escalar eficientemente a un número grande de
vistas~\cite{arvelo:aaai06,pods:DuschkaG97,sac:DuschkaG97,levy:bucket,pottinger:minicon}.
En este trabajo se propone la infraestructura {\it MCDSat}$^c$ que extiende la
aproximación propuesta en  ~\cite{arvelo:aaai06}, con la capacidad de trabajar
con constantes y de identificar la composición de servicios que maximice una
función de utilidad dada.

{\it MCDSat}$^c$  traduce una instancia del problema de selección de servicios
en el problema de enumerar los modelos de una teoría proposicional que codifica
información sobre el flujo de trabajo, los servicios concretos y las condiciones
que deben ser satisfechas para generar una composición que maximice la función
de utilidad. Esta teoría se representa como una fórmula CNF que es compilada a
su representación d-DNNF, a partir de la cual los modelos que maximicen la
función global de utilidad se obtienen en tiempo lineal usando técnicas modernas
de SAT~\cite{darwiche:dnnf}. Se estudia empíricamente la calidad de {\it
MCDSat}$^c$ sobre una variedad de \emph{benchmarks} y se observa que la técnica
propuesta provee una solución eficiente al problema de selección de servicios
que es capaz de escalar a flujos de trabajo grandes así como a números de vistas
grandes.

@@

\section{Motivación}

Consideremos los servicios abstractos y concretos en la tabla
~\ref{table:services} que representan aplicaciones en el dominio de vuelos.

\begin{table}
\begin{tabular}{| l| l |}
\hline
Servicio Abstracto & Descripción \\
\hline
$fight(x1,x2)$ & relaciona las ciudades x1 y x2 si hay un vuelo entre ellas\\
\hline
$uscity(x1)$ &  determina si una ciudad x1 es una ciudad de Estados Unidos\\
\hline \hline
Servicio Concreto & Descripción \\
\hline
$national(x1,y1)$&  retorna dos ciudades de Estados Unidos que están conectadas
por vuelos directos \\
\hline
$oneway(x1,y1)$ & retorna dos ciudades que están conectadas por vuelos directos
de ida\\
\hline
$onestop(x1,y1)$ & retorna dos ciudades que están conectadas por vuelos con una
escala\\
\hline
$ flightToCCS(x1,"CCS")$ & retorna una ciudad que está conectada a Caracas por
un vuelo directo\\
 \hline
$ onestopToCCS(x1,y1)$ & retorna dos ciudades x1 y y1 tales que hay un vuelo con
una escala desde la ciudad x1 hasta Caracas con parada en la ciudad y1\\
 \hline
 $fromWAS("WAS",y1)$ &  retorna una ciudad y1 a la cual llegan vuelos desde
Washington.\\
 \hline
\end{tabular}
\label{table:services}
\caption{Servicios Abstractos y Concretos}
\end{table}

@@

\begin{figure}
\centering
%\includegraphics[width=8cm]{odd}
\caption{A decomposable and deterministic NNF.}
\label{fig:dnnf}
\end{figure}

@@

In order to do so, the theory $\Theory{\Q}$ is transformed into a d-DNNF
theory $\Delta(\Q)$ with a CNF to d-DNNF compiler.
The compiler's algorithm is similar to the DPLL algorithm
for SAT but enhanced with advanced techniques such as clause
learning and caching.
\begin{figure}
\centering
%COMENTADO\includegraphics[width=10cm]{mdcsatC.pdf}
\caption{The McdSat$^c$ Architecture}
\label{fig:dnnf}
\end{figure}

@@

\begin{figure}
\centering
%COMENTADO\includegraphics[width=8cm]{plot1.pdf}
\caption{Compilation Time Benchmark I}
\label{fig:plot1}
\end{figure}
